---
title: "MasterWide"
author: "Enrico Indiogine"
date: "March 6, 2016"
output: 
  word_document: 
    fig_height: 10
---

In this document I show a possible way to analyze the MasterWide data from the file *MasterWide_StudyVI_TestScores_Sample.xlsx*.
Also, for now I will only analyze the pre-test data.  The code for the data management and these analyses is found in the file *TAMU.R*.

## Step 1 - General settings and load libraries
```{r step-1, echo=FALSE, message=FALSE}
require(xlsx)
require(dplyr)
require(ggplot2)
require(reshape2)
require(likert)
require(betareg)

# General settings
options(scipen=999)
options(show.signif.stars=FALSE)
tau <- 2 * pi
rm(list=ls(all=TRUE))
```
## Step 2 - Load and clean data
Then we load the data from the xlsx file and prepare the data.  We remove the missing data rows and convert the original coding of "-1", "0", and "1" to "incorrect", "unknown", and "correct".
```{r step-2, echo=FALSE}
# Project specific settings
filename <- "MasterWide_StudyVI_TestScores_Sample.xlsx"
setwd("/home/henk/Code/MasterWide")

# Load data and remove NAs
temp <- read.xlsx(file = filename, sheetName = "MasterWide_StudyVI_TestScores")
data_raw <- na.omit(temp)
rm(temp)

# Shorten column names (predictors). 
data_pre <- data.frame(Condition = data_raw$Condition.Name,
                  problem1_opt_1 = as.character(data_raw$Pre.Test.LT_problem1_option1),
                  problem1_opt_2 = as.character(data_raw$Pre.Test.LT_problem1_option2),
                  problem1_opt_3 = as.character(data_raw$Pre.Test.LT_problem1_option3),
                  problem1_opt_4 = as.character(data_raw$Pre.Test.LT_problem1_option4),
                  problem1_opt_5 = as.character(data_raw$Pre.Test.LT_problem1_option5),
                  problem1_opt_6 = as.character(data_raw$Pre.Test.LT_problem1_option6),
                  problem2_opt_1 = as.character(data_raw$Pre.Test.LT_problem2_option1),
                  problem2_opt_2 = as.character(data_raw$Pre.Test.LT_problem2_option2),
                  problem2_opt_3 = as.character(data_raw$Pre.Test.LT_problem2_option3),
                  problem2_opt_4 = as.character(data_raw$Pre.Test.LT_problem2_option4),
                  problem2_opt_5 = as.character(data_raw$Pre.Test.LT_problem2_option5),
                  problem2_opt_6 = as.character(data_raw$Pre.Test.LT_problem2_option6),
                  eq_problem1    = as.character(data_raw$Pre.Test.eq_problem1_box),
                  eq_problem2    = as.character(data_raw$Pre.Test.eq_problem2_box),
                  eq_problem3    = as.character(data_raw$Pre.Test.eq_problem3_box),
                  eq_problem4    = as.character(data_raw$Pre.Test.eq_problem4_box),
                  eq_problem5    = as.character(data_raw$Pre.Test.eq_problem5_box),
                  eq_problem6    = as.character(data_raw$Pre.Test.eq_problem6_box),
                  eq_problem7    = as.character(data_raw$Pre.Test.eq_problem7_box),
                  eq_problem8    = as.character(data_raw$Pre.Test.eq_problem8_box),
                  eq_problem9    = as.character(data_raw$Pre.Test.eq_problem9_box))

# Create a copy for later analysis
data_raw_pre <- data_pre

# Convert numbers to their meaning
data_pre$problem1_opt_1 <- gsub("-1","incorrect", data_pre$problem1_opt_1)
data_pre$problem1_opt_1 <- gsub("0","unknown", data_pre$problem1_opt_1)
data_pre$problem1_opt_1 <- gsub("1","correct", data_pre$problem1_opt_1)

data_pre$problem1_opt_2 <- gsub("-1","incorrect", data_pre$problem1_opt_2)
data_pre$problem1_opt_2 <- gsub("0","unknown", data_pre$problem1_opt_2)
data_pre$problem1_opt_2 <- gsub("1","correct", data_pre$problem1_opt_2)

data_pre$problem1_opt_3 <- gsub("-1","incorrect", data_pre$problem1_opt_3)
data_pre$problem1_opt_3 <- gsub("0","unknown", data_pre$problem1_opt_3)
data_pre$problem1_opt_3 <- gsub("1","correct", data_pre$problem1_opt_3)

data_pre$problem1_opt_4 <- gsub("-1","incorrect", data_pre$problem1_opt_4)
data_pre$problem1_opt_4 <- gsub("0","unknown", data_pre$problem1_opt_4)
data_pre$problem1_opt_4 <- gsub("1","correct", data_pre$problem1_opt_4)

data_pre$problem1_opt_5 <- gsub("-1","incorrect", data_pre$problem1_opt_5)
data_pre$problem1_opt_5 <- gsub("0","unknown", data_pre$problem1_opt_5)
data_pre$problem1_opt_5 <- gsub("1","correct", data_pre$problem1_opt_5)

data_pre$problem1_opt_6 <- gsub("-1","incorrect", data_pre$problem1_opt_6)
data_pre$problem1_opt_6 <- gsub("0","unknown", data_pre$problem1_opt_6)
data_pre$problem1_opt_6 <- gsub("1","correct", data_pre$problem1_opt_6)

data_pre$problem2_opt_1 <- gsub("-1","incorrect", data_pre$problem2_opt_1)
data_pre$problem2_opt_1 <- gsub("0","unknown", data_pre$problem2_opt_1)
data_pre$problem2_opt_1 <- gsub("1","correct", data_pre$problem2_opt_1)

data_pre$problem2_opt_2 <- gsub("-1","incorrect", data_pre$problem2_opt_2)
data_pre$problem2_opt_2 <- gsub("0","unknown", data_pre$problem2_opt_2)
data_pre$problem2_opt_2 <- gsub("1","correct", data_pre$problem2_opt_2)

data_pre$problem2_opt_3 <- gsub("-1","incorrect", data_pre$problem2_opt_3)
data_pre$problem2_opt_3 <- gsub("0","unknown", data_pre$problem2_opt_3)
data_pre$problem2_opt_3 <- gsub("1","correct", data_pre$problem2_opt_3)

data_pre$problem2_opt_4 <- gsub("-1","incorrect", data_pre$problem2_opt_4)
data_pre$problem2_opt_4 <- gsub("0","unknown", data_pre$problem2_opt_4)
data_pre$problem2_opt_4 <- gsub("1","correct", data_pre$problem2_opt_4)

data_pre$problem2_opt_5 <- gsub("-1","incorrect", data_pre$problem2_opt_5)
data_pre$problem2_opt_5 <- gsub("0","unknown", data_pre$problem2_opt_5)
data_pre$problem2_opt_5 <- gsub("1","correct", data_pre$problem2_opt_5)

data_pre$problem2_opt_6 <- gsub("-1","incorrect", data_pre$problem2_opt_6)
data_pre$problem2_opt_6 <- gsub("0","unknown", data_pre$problem2_opt_6)
data_pre$problem2_opt_6 <- gsub("1","correct", data_pre$problem2_opt_6)

data_pre$eq_problem1 <- gsub("-1","incorrect", data_pre$eq_problem1)
data_pre$eq_problem1 <- gsub("0","unknown", data_pre$eq_problem1)
data_pre$eq_problem1 <- gsub("1","correct", data_pre$eq_problem1)

data_pre$eq_problem2 <- gsub("-1","incorrect", data_pre$eq_problem2)
data_pre$eq_problem2 <- gsub("0","unknown", data_pre$eq_problem2)
data_pre$eq_problem2 <- gsub("1","correct", data_pre$eq_problem2)

data_pre$eq_problem3 <- gsub("-1","incorrect", data_pre$eq_problem3)
data_pre$eq_problem3 <- gsub("0","unknown", data_pre$eq_problem3)
data_pre$eq_problem3 <- gsub("1","correct", data_pre$eq_problem3)

data_pre$eq_problem4 <- gsub("-1","incorrect", data_pre$eq_problem4)
data_pre$eq_problem4 <- gsub("0","unknown", data_pre$eq_problem4)
data_pre$eq_problem4 <- gsub("1","correct", data_pre$eq_problem4)

data_pre$eq_problem5 <- gsub("-1","incorrect", data_pre$eq_problem5)
data_pre$eq_problem5 <- gsub("0","unknown", data_pre$eq_problem5)
data_pre$eq_problem5 <- gsub("1","correct", data_pre$eq_problem5)

data_pre$eq_problem6 <- gsub("-1","incorrect", data_pre$eq_problem6)
data_pre$eq_problem6 <- gsub("0","unknown", data_pre$eq_problem6)
data_pre$eq_problem6 <- gsub("1","correct", data_pre$eq_problem6)

data_pre$eq_problem7 <- gsub("-1","incorrect", data_pre$eq_problem7)
data_pre$eq_problem7 <- gsub("0","unknown", data_pre$eq_problem7)
data_pre$eq_problem7 <- gsub("1","correct", data_pre$eq_problem7)

data_pre$eq_problem8 <- gsub("-1","incorrect", data_pre$eq_problem8)
data_pre$eq_problem8 <- gsub("0","unknown", data_pre$eq_problem8)
data_pre$eq_problem8 <- gsub("1","correct", data_pre$eq_problem8)

data_pre$eq_problem9 <- gsub("-1","incorrect", data_pre$eq_problem9)
data_pre$eq_problem9 <- gsub("0","unknown", data_pre$eq_problem9)
data_pre$eq_problem9 <- gsub("1","correct", data_pre$eq_problem9)

# Convert to factor and adjust levels.
data_pre$problem1_opt_1 <- factor(data_pre$problem1_opt_1, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_pre$problem1_opt_2 <- factor(data_pre$problem1_opt_2, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_pre$problem1_opt_3 <- factor(data_pre$problem1_opt_3, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_pre$problem1_opt_4 <- factor(data_pre$problem1_opt_4, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_pre$problem1_opt_5 <- factor(data_pre$problem1_opt_5, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_pre$problem1_opt_6 <- factor(data_pre$problem1_opt_6, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_pre$problem2_opt_1 <- factor(data_pre$problem2_opt_1, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_pre$problem2_opt_2 <- factor(data_pre$problem2_opt_2, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_pre$problem2_opt_3 <- factor(data_pre$problem2_opt_3, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_pre$problem2_opt_4 <- factor(data_pre$problem2_opt_4, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_pre$problem2_opt_5 <- factor(data_pre$problem2_opt_5, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_pre$problem2_opt_6 <- factor(data_pre$problem2_opt_6, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_pre$eq_problem1    <- factor(data_pre$eq_problem1, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_pre$eq_problem2    <- factor(data_pre$eq_problem2, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_pre$eq_problem3    <- factor(data_pre$eq_problem3, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_pre$eq_problem4    <- factor(data_pre$eq_problem4, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_pre$eq_problem5    <- factor(data_pre$eq_problem5, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_pre$eq_problem6    <- factor(data_pre$eq_problem6, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_pre$eq_problem7    <- factor(data_pre$eq_problem7, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_pre$eq_problem8    <- factor(data_pre$eq_problem8, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_pre$eq_problem9    <- factor(data_pre$eq_problem9, ordered=TRUE, levels = c("incorrect","unknown","correct"))
#####################################################################################################
data_post <- data.frame(Condition = data_raw$Condition.Name,
                        problem1_opt_1 = as.character(data_raw$Post.Test.LT_problem1_option1),
                        problem1_opt_2 = as.character(data_raw$Post.Test.LT_problem1_option2),
                        problem1_opt_3 = as.character(data_raw$Post.Test.LT_problem1_option3),
                        problem1_opt_4 = as.character(data_raw$Post.Test.LT_problem1_option4),
                        problem1_opt_5 = as.character(data_raw$Post.Test.LT_problem1_option5),
                        problem1_opt_6 = as.character(data_raw$Post.Test.LT_problem1_option6),
                        problem2_opt_1 = as.character(data_raw$Post.Test.LT_problem2_option1),
                        problem2_opt_2 = as.character(data_raw$Post.Test.LT_problem2_option2),
                        problem2_opt_3 = as.character(data_raw$Post.Test.LT_problem2_option3),
                        problem2_opt_4 = as.character(data_raw$Post.Test.LT_problem2_option4),
                        problem2_opt_5 = as.character(data_raw$Post.Test.LT_problem2_option5),
                        problem2_opt_6 = as.character(data_raw$Post.Test.LT_problem2_option6),
                        eq_problem1    = as.character(data_raw$Post.Test.eq_problem1_box),
                        eq_problem2    = as.character(data_raw$Post.Test.eq_problem2_box),
                        eq_problem3    = as.character(data_raw$Post.Test.eq_problem3_box),
                        eq_problem4    = as.character(data_raw$Post.Test.eq_problem4_box),
                        eq_problem5    = as.character(data_raw$Post.Test.eq_problem5_box),
                        eq_problem6    = as.character(data_raw$Post.Test.eq_problem6_box),
                        eq_problem7    = as.character(data_raw$Post.Test.eq_problem7_box),
                        eq_problem8    = as.character(data_raw$Post.Test.eq_problem8_box),
                        eq_problem9    = as.character(data_raw$Post.Test.eq_problem9_box))

# Create a copy for later analysis
data_raw_post <- data_post

data_post$problem1_opt_1 <- gsub("-1","incorrect", data_post$problem1_opt_1)
data_post$problem1_opt_1 <- gsub("0","unknown", data_post$problem1_opt_1)
data_post$problem1_opt_1 <- gsub("1","correct", data_post$problem1_opt_1)

data_post$problem1_opt_2 <- gsub("-1","incorrect", data_post$problem1_opt_2)
data_post$problem1_opt_2 <- gsub("0","unknown", data_post$problem1_opt_2)
data_post$problem1_opt_2 <- gsub("1","correct", data_post$problem1_opt_2)

data_post$problem1_opt_3 <- gsub("-1","incorrect", data_post$problem1_opt_3)
data_post$problem1_opt_3 <- gsub("0","unknown", data_post$problem1_opt_3)
data_post$problem1_opt_3 <- gsub("1","correct", data_post$problem1_opt_3)

data_post$problem1_opt_4 <- gsub("-1","incorrect", data_post$problem1_opt_4)
data_post$problem1_opt_4 <- gsub("0","unknown", data_post$problem1_opt_4)
data_post$problem1_opt_4 <- gsub("1","correct", data_post$problem1_opt_4)

data_post$problem1_opt_5 <- gsub("-1","incorrect", data_post$problem1_opt_5)
data_post$problem1_opt_5 <- gsub("0","unknown", data_post$problem1_opt_5)
data_post$problem1_opt_5 <- gsub("1","correct", data_post$problem1_opt_5)

data_post$problem1_opt_6 <- gsub("-1","incorrect", data_post$problem1_opt_6)
data_post$problem1_opt_6 <- gsub("0","unknown", data_post$problem1_opt_6)
data_post$problem1_opt_6 <- gsub("1","correct", data_post$problem1_opt_6)

data_post$problem2_opt_1 <- gsub("-1","incorrect", data_post$problem2_opt_1)
data_post$problem2_opt_1 <- gsub("0","unknown", data_post$problem2_opt_1)
data_post$problem2_opt_1 <- gsub("1","correct", data_post$problem2_opt_1)

data_post$problem2_opt_2 <- gsub("-1","incorrect", data_post$problem2_opt_2)
data_post$problem2_opt_2 <- gsub("0","unknown", data_post$problem2_opt_2)
data_post$problem2_opt_2 <- gsub("1","correct", data_post$problem2_opt_2)

data_post$problem2_opt_3 <- gsub("-1","incorrect", data_post$problem2_opt_3)
data_post$problem2_opt_3 <- gsub("0","unknown", data_post$problem2_opt_3)
data_post$problem2_opt_3 <- gsub("1","correct", data_post$problem2_opt_3)

data_post$problem2_opt_4 <- gsub("-1","incorrect", data_post$problem2_opt_4)
data_post$problem2_opt_4 <- gsub("0","unknown", data_post$problem2_opt_4)
data_post$problem2_opt_4 <- gsub("1","correct", data_post$problem2_opt_4)

data_post$problem2_opt_5 <- gsub("-1","incorrect", data_post$problem2_opt_5)
data_post$problem2_opt_5 <- gsub("0","unknown", data_post$problem2_opt_5)
data_post$problem2_opt_5 <- gsub("1","correct", data_post$problem2_opt_5)

data_post$problem2_opt_6 <- gsub("-1","incorrect", data_post$problem2_opt_6)
data_post$problem2_opt_6 <- gsub("0","unknown", data_post$problem2_opt_6)
data_post$problem2_opt_6 <- gsub("1","correct", data_post$problem2_opt_6)

data_post$eq_problem1 <- gsub("-1","incorrect", data_post$eq_problem1)
data_post$eq_problem1 <- gsub("0","unknown", data_post$eq_problem1)
data_post$eq_problem1 <- gsub("1","correct", data_post$eq_problem1)

data_post$eq_problem2 <- gsub("-1","incorrect", data_post$eq_problem2)
data_post$eq_problem2 <- gsub("0","unknown", data_post$eq_problem2)
data_post$eq_problem2 <- gsub("1","correct", data_post$eq_problem2)

data_post$eq_problem3 <- gsub("-1","incorrect", data_post$eq_problem3)
data_post$eq_problem3 <- gsub("0","unknown", data_post$eq_problem3)
data_post$eq_problem3 <- gsub("1","correct", data_post$eq_problem3)

data_post$eq_problem4 <- gsub("-1","incorrect", data_post$eq_problem4)
data_post$eq_problem4 <- gsub("0","unknown", data_post$eq_problem4)
data_post$eq_problem4 <- gsub("1","correct", data_post$eq_problem4)

data_post$eq_problem5 <- gsub("-1","incorrect", data_post$eq_problem5)
data_post$eq_problem5 <- gsub("0","unknown", data_post$eq_problem5)
data_post$eq_problem5 <- gsub("1","correct", data_post$eq_problem5)

data_post$eq_problem6 <- gsub("-1","incorrect", data_post$eq_problem6)
data_post$eq_problem6 <- gsub("0","unknown", data_post$eq_problem6)
data_post$eq_problem6 <- gsub("1","correct", data_post$eq_problem6)

data_post$eq_problem7 <- gsub("-1","incorrect", data_post$eq_problem7)
data_post$eq_problem7 <- gsub("0","unknown", data_post$eq_problem7)
data_post$eq_problem7 <- gsub("1","correct", data_post$eq_problem7)

data_post$eq_problem8 <- gsub("-1","incorrect", data_post$eq_problem8)
data_post$eq_problem8 <- gsub("0","unknown", data_post$eq_problem8)
data_post$eq_problem8 <- gsub("1","correct", data_post$eq_problem8)

data_post$eq_problem9 <- gsub("-1","incorrect", data_post$eq_problem9)
data_post$eq_problem9 <- gsub("0","unknown", data_post$eq_problem9)
data_post$eq_problem9 <- gsub("1","correct", data_post$eq_problem9)

data_post$problem1_opt_1 <- factor(data_post$problem1_opt_1, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_post$problem1_opt_2 <- factor(data_post$problem1_opt_2, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_post$problem1_opt_3 <- factor(data_post$problem1_opt_3, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_post$problem1_opt_4 <- factor(data_post$problem1_opt_4, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_post$problem1_opt_5 <- factor(data_post$problem1_opt_5, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_post$problem1_opt_6 <- factor(data_post$problem1_opt_6, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_post$problem2_opt_1 <- factor(data_post$problem2_opt_1, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_post$problem2_opt_2 <- factor(data_post$problem2_opt_2, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_post$problem2_opt_3 <- factor(data_post$problem2_opt_3, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_post$problem2_opt_4 <- factor(data_post$problem2_opt_4, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_post$problem2_opt_5 <- factor(data_post$problem2_opt_5, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_post$problem2_opt_6 <- factor(data_post$problem2_opt_6, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_post$eq_problem1    <- factor(data_post$eq_problem1, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_post$eq_problem2    <- factor(data_post$eq_problem2, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_post$eq_problem3    <- factor(data_post$eq_problem3, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_post$eq_problem4    <- factor(data_post$eq_problem4, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_post$eq_problem5    <- factor(data_post$eq_problem5, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_post$eq_problem6    <- factor(data_post$eq_problem6, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_post$eq_problem7    <- factor(data_post$eq_problem7, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_post$eq_problem8    <- factor(data_post$eq_problem7, ordered=TRUE, levels = c("incorrect","unknown","correct"))
data_post$eq_problem9    <- factor(data_post$eq_problem7, ordered=TRUE, levels = c("incorrect","unknown","correct"))
```
## Step 3 - Summary of raw data
Here we see a table with summaries of the data:
```{r step-3, echo=FALSE}
print("Pre-test data")
print(table(data_pre$Condition))

print("Post-test data")
print(table(data_post$Condition))
```

## Step 4 - Create and Plot the Likert objects
The Likert plots are grouped by Condition. There are too many rows for all items, thus I break up the Likert object by the 3 problems, "Problem1", "Problem2", and "Eq_Problem". In addition, I shorten the variable names for the sake of legibility.
```{r step-4, echo=FALSE}
problem_1_pre <- select(data_pre, Condition, problem1_opt_1, problem1_opt_2, problem1_opt_3,
                                             problem1_opt_4, problem1_opt_5, problem1_opt_6)
problem_1_pre_likert <- likert(problem_1_pre[2:7], grouping = problem_1_pre$Condition)
plot(problem_1_pre_likert, center=2.5, ggtitle = "Problem 1, pre-test")
ggsave(filename = "Problem_1_pre.png") 

problem_2_pre <- select(data_pre, Condition, problem2_opt_1, problem2_opt_2, problem2_opt_3,
                        problem2_opt_4, problem2_opt_5, problem2_opt_6)
problem_2_pre_likert <- likert(problem_2_pre[2:7], grouping = problem_2_pre$Condition)
plot(problem_2_pre_likert, center=2.5, ggtitle = "Problem 2, pre-test")
ggsave(filename = "Problem_2_pre.png")

eq_problem_pre <- select(data_pre, Condition, eq_problem1, eq_problem2, eq_problem3,
                         eq_problem4, eq_problem5, eq_problem6, eq_problem7, eq_problem8, eq_problem9)
eq_problem_pre_likert <- likert(eq_problem_pre[2:10], grouping = eq_problem_pre$Condition)
plot(eq_problem_pre_likert, center=2.5, ggtitle = "Eq Problem, pre-test")
ggsave(filename = "Eq_Problem_pre.png", height=10)
```

## Step 5 - Statistical test for equality of proportions
Since we are looking at the pre-test data, we need to assure that they are fairly homogeneous among conditions before the treatment.  Because the number of rows is unequal between conditions we should not use ANOVA or something similar.  We should convert the data to proportions and test for equality of proportion.  I do this using the Beta regression test, see: https://cran.r-project.org/web/packages/betareg/vignettes/betareg.pdf

For this analysis I convert the "unknown" and "incorrect" responses to zero and "correct" to one.

For ease of interpretation I also perform a two-way test of equality of proportion using the Chi-square test.

```{r step-5, echo=FALSE}
data_pre_prop <- data.frame(Condition = data_raw$Condition.Name,
                       problem1_opt_1 = as.character(data_raw$Pre.Test.LT_problem1_option1),
                       problem1_opt_2 = as.character(data_raw$Pre.Test.LT_problem1_option2),
                       problem1_opt_3 = as.character(data_raw$Pre.Test.LT_problem1_option3),
                       problem1_opt_4 = as.character(data_raw$Pre.Test.LT_problem1_option4),
                       problem1_opt_5 = as.character(data_raw$Pre.Test.LT_problem1_option5),
                       problem1_opt_6 = as.character(data_raw$Pre.Test.LT_problem1_option6),
                       problem2_opt_1 = as.character(data_raw$Pre.Test.LT_problem2_option1),
                       problem2_opt_2 = as.character(data_raw$Pre.Test.LT_problem2_option2),
                       problem2_opt_3 = as.character(data_raw$Pre.Test.LT_problem2_option3),
                       problem2_opt_4 = as.character(data_raw$Pre.Test.LT_problem2_option4),
                       problem2_opt_5 = as.character(data_raw$Pre.Test.LT_problem2_option5),
                       problem2_opt_6 = as.character(data_raw$Pre.Test.LT_problem2_option6),
                       eq_problem1    = as.character(data_raw$Pre.Test.eq_problem1_box),
                       eq_problem2    = as.character(data_raw$Pre.Test.eq_problem2_box),
                       eq_problem3    = as.character(data_raw$Pre.Test.eq_problem3_box),
                       eq_problem4    = as.character(data_raw$Pre.Test.eq_problem4_box),
                       eq_problem5    = as.character(data_raw$Pre.Test.eq_problem5_box),
                       eq_problem6    = as.character(data_raw$Pre.Test.eq_problem6_box),
                       eq_problem7    = as.character(data_raw$Pre.Test.eq_problem7_box),
                       eq_problem8    = as.character(data_raw$Pre.Test.eq_problem8_box),
                       eq_problem9    = as.character(data_raw$Pre.Test.eq_problem9_box))

# Convert numbers to one for correct and zero otherwise
#
data_pre_prop$problem1_opt_1 <- gsub("-1","0", data_pre_prop$problem1_opt_1)
data_pre_prop$problem1_opt_2 <- gsub("-1","0", data_pre_prop$problem1_opt_2)
data_pre_prop$problem1_opt_3 <- gsub("-1","0", data_pre_prop$problem1_opt_3)
data_pre_prop$problem1_opt_4 <- gsub("-1","0", data_pre_prop$problem1_opt_4)
data_pre_prop$problem1_opt_5 <- gsub("-1","0", data_pre_prop$problem1_opt_5)
data_pre_prop$problem1_opt_6 <- gsub("-1","0", data_pre_prop$problem1_opt_6)
data_pre_prop$problem2_opt_1 <- gsub("-1","0", data_pre_prop$problem2_opt_1)
data_pre_prop$problem2_opt_2 <- gsub("-1","0", data_pre_prop$problem2_opt_2)
data_pre_prop$problem2_opt_3 <- gsub("-1","0", data_pre_prop$problem2_opt_3)
data_pre_prop$problem2_opt_4 <- gsub("-1","0", data_pre_prop$problem2_opt_4)
data_pre_prop$problem2_opt_5 <- gsub("-1","0", data_pre_prop$problem2_opt_5)
data_pre_prop$problem2_opt_6 <- gsub("-1","0", data_pre_prop$problem2_opt_6)
data_pre_prop$eq_problem1    <- gsub("-1","0", data_pre_prop$eq_problem1)
data_pre_prop$eq_problem2    <- gsub("-1","0", data_pre_prop$eq_problem2)
data_pre_prop$eq_problem3    <- gsub("-1","0", data_pre_prop$eq_problem3)
data_pre_prop$eq_problem4    <- gsub("-1","0", data_pre_prop$eq_problem4)
data_pre_prop$eq_problem5    <- gsub("-1","0", data_pre_prop$eq_problem5)
data_pre_prop$eq_problem6    <- gsub("-1","0", data_pre_prop$eq_problem6)
data_pre_prop$eq_problem7    <- gsub("-1","0", data_pre_prop$eq_problem7)
data_pre_prop$eq_problem8    <- gsub("-1","0", data_pre_prop$eq_problem8)
data_pre_prop$eq_problem9    <- gsub("-1","0", data_pre_prop$eq_problem9)

# data_pre_prop <- data.frame(data_pre$Condition, apply(data_pre_prop[2:22], 2, as.integer))
temp_1 <- sapply(data_pre_prop[, 2:22], as.numeric)
temp_2 <- data.frame(temp_1)

data_pre_prop <- cbind(data_pre_prop$Condition, temp_2)
names(data_pre_prop)[names(data_pre_prop) == 'data_pre_prop$Condition'] <- 'Condition'
rm(temp_1, temp_2)

data_pre_prop_metatutor   <- filter(data_pre_prop, Condition == "MetaTutor")
data_pre_prop_metatutorc  <- filter(data_pre_prop, Condition == "MetaTutorC")
data_pre_prop_metatutormc <- filter(data_pre_prop, Condition == "MetaTutorMC")

metatutor_sums   <- colSums(data_pre_prop_metatutor[2:22])
metatutorc_sums  <- colSums(data_pre_prop_metatutorc[2:22])
metatutormc_sums <- colSums(data_pre_prop_metatutormc[2:22])

metatutor_count   <- dim(data_pre_prop_metatutor)[1]
metatutorc_count  <- dim(data_pre_prop_metatutorc)[1]
metatutormc_count <- dim(data_pre_prop_metatutormc)[1]

metatutor_prop   <- metatutor_sums / metatutor_count
metatutorc_prop  <- metatutorc_sums / metatutorc_count
metatutormc_prop <- metatutormc_sums / metatutormc_count

temp_3 <- rbind(metatutor_prop, metatutorc_prop, metatutormc_prop)
temp_4 <- data.frame(temp_3)
Condition <- c("MetaTutor", "MetaTutorC", "MetaTutorMC")
temp_5 <- cbind(Condition, temp_4)
data_pre_proportion <- melt(temp_5, id = "Condition")
rm(temp_3, temp_4, temp_5)

beta_pre <- betareg(data=data_pre_proportion, value ~ Condition - 1, hessian = TRUE)
summary(beta_pre)

# Test of equality of proportions for each outcome variable
# This has to be done pairwise
# Compare first MetaTutor and MetaTutorC.
#
print("MetaTutor vs. MetaTutorC")
for (i in 1:21)
{
  temp_prop <- prop.test(x = c(metatutor_sums[i], metatutorc_sums[i]), n = c(metatutor_count, metatutorc_count) )
  print(names(metatutor_sums)[i])
  print(temp_prop)
}

# Then we compare Metatutor with MetaTutorMC
print("MetaTutor vs. MetaTutorMC")
for (i in 1:21)
{
  temp_prop <- prop.test(x = c(metatutor_sums[i], metatutormc_sums[i]), n = c(metatutor_count, metatutormc_count) )
  print(names(metatutor_sums)[i])
  print(temp_prop)
}

# Finally we compare MetatutorC with MetaTutorMC
print("MetaTutorC vs. MetaTutorMC")
for (i in 1:21)
{
  temp_prop <- prop.test(x = c(metatutorc_sums[i], metatutormc_sums[i]), n = c(metatutorc_count, metatutormc_count) )
  print(names(metatutor_sums)[i])
  print(temp_prop)
}
```
We can see that none of the Chi-square test gives a p-value below 5%. By visually inspecting the Likert plots we can also deduce that there are no obvious differences between the conditions as we expected because these are pre-treament data.

## Step 6 - Calculate, show and assess the effect of the conditions
One way to show the effects of the different conditions is to calculate the "shift", that is, the difference between the post- and the pre-test.  Hence we can measure the effect of the treatment.  Also this shift can be represented by Likert plots.

```{r step-6, echo=FALSE}
# Create dataframe with differences
shift.df <- data.frame(Condition = data_raw$Condition.Name,
                  problem1_opt_1 = factor(as.numeric(data_raw_post[,2]) - as.numeric(data_raw_pre[,2]), ordered = TRUE, levels=c('-2','-1','0','1','2')),
                  problem1_opt_2 = factor(as.numeric(data_raw_post[,3]) - as.numeric(data_raw_pre[,3]), ordered = TRUE, levels=c('-2','-1','0','1','2')),
                  problem1_opt_3 = factor(as.numeric(data_raw_post[,4]) - as.numeric(data_raw_pre[,4]), ordered = TRUE, levels=c('-2','-1','0','1','2')),
                  problem1_opt_4 = factor(as.numeric(data_raw_post[,5]) - as.numeric(data_raw_pre[,5]), ordered = TRUE, levels=c('-2','-1','0','1','2')),
                  problem1_opt_5 = factor(as.numeric(data_raw_post[,6]) - as.numeric(data_raw_pre[,6]), ordered = TRUE, levels=c('-2','-1','0','1','2')),
                  problem1_opt_6 = factor(as.numeric(data_raw_post[,7]) - as.numeric(data_raw_pre[,7]), ordered = TRUE, levels=c('-2','-1','0','1','2')),
                  problem2_opt_1 = factor(as.numeric(data_raw_post[,8]) - as.numeric(data_raw_pre[,8]), ordered = TRUE, levels=c('-2','-1','0','1','2')),
                  problem2_opt_2 = factor(as.numeric(data_raw_post[,9]) - as.numeric(data_raw_pre[,9]), ordered = TRUE, levels=c('-2','-1','0','1','2')),
                  problem2_opt_3 = factor(as.numeric(data_raw_post[,10]) - as.numeric(data_raw_pre[,10]), ordered = TRUE, levels=c('-2','-1','0','1','2')),
                  problem2_opt_4 = factor(as.numeric(data_raw_post[,11]) - as.numeric(data_raw_pre[,11]), ordered = TRUE, levels=c('-2','-1','0','1','2')),
                  problem2_opt_5 = factor(as.numeric(data_raw_post[,12]) - as.numeric(data_raw_pre[,12]), ordered = TRUE, levels=c('-2','-1','0','1','2')),
                  problem2_opt_6 = factor(as.numeric(data_raw_post[,13]) - as.numeric(data_raw_pre[,13]), ordered = TRUE, levels=c('-2','-1','0','1','2')),
                  eq_problem1    = factor(as.numeric(data_raw_post[,14]) - as.numeric(data_raw_pre[,14]), ordered = TRUE, levels=c('-2','-1','0','1','2')),
                  eq_problem2    = factor(as.numeric(data_raw_post[,15]) - as.numeric(data_raw_pre[,15]), ordered = TRUE, levels=c('-2','-1','0','1','2')),
                  eq_problem3    = factor(as.numeric(data_raw_post[,16]) - as.numeric(data_raw_pre[,16]), ordered = TRUE, levels=c('-2','-1','0','1','2')),
                  eq_problem4    = factor(as.numeric(data_raw_post[,17]) - as.numeric(data_raw_pre[,17]), ordered = TRUE, levels=c('-2','-1','0','1','2')),
                  eq_problem5    = factor(as.numeric(data_raw_post[,18]) - as.numeric(data_raw_pre[,18]), ordered = TRUE, levels=c('-2','-1','0','1','2')),
                  eq_problem6    = factor(as.numeric(data_raw_post[,19]) - as.numeric(data_raw_pre[,19]), ordered = TRUE, levels=c('-2','-1','0','1','2')),
                  eq_problem7    = factor(as.numeric(data_raw_post[,20]) - as.numeric(data_raw_pre[,20]), ordered = TRUE, levels=c('-2','-1','0','1','2')),
                  eq_problem8    = factor(as.numeric(data_raw_post[,21]) - as.numeric(data_raw_pre[,21]), ordered = TRUE, levels=c('-2','-1','0','1','2')),
                  eq_problem9    = factor(as.numeric(data_raw_post[,22]) - as.numeric(data_raw_pre[,22]), ordered = TRUE, levels=c('-2','-1','0','1','2')))

# We can plot these shifts as Likert objects
problem_1_shift <- select(shift.df, Condition, problem1_opt_1, problem1_opt_2, problem1_opt_3,
                                               problem1_opt_4, problem1_opt_5, problem1_opt_6)
problem_1_shift_likert <- likert(problem_1_shift[2:7], grouping = problem_1_shift$Condition)
plot(problem_1_shift_likert, center=3, ggtitle = "Problem 1, shifts")
ggsave(filename = "Problem_1_shift.png", height=6) 

problem_2_shift <- select(shift.df, Condition, problem2_opt_1, problem2_opt_2, problem2_opt_3,
                                               problem2_opt_4, problem2_opt_5, problem2_opt_6)
problem_2_shift_likert <- likert(problem_2_shift[2:7], grouping = problem_2_shift$Condition)
plot(problem_2_shift_likert, center=3, ggtitle = "Problem 2, shifts")
ggsave(filename = "Problem_2_shift.png", height=6)

eq_problem_shift <- select(shift.df, Condition, eq_problem1, eq_problem2, eq_problem3, eq_problem4,
                                                eq_problem5, eq_problem6, eq_problem7, eq_problem8, eq_problem9)
eq_problem_shift_likert <- likert(eq_problem_shift[2:10], grouping = eq_problem_shift$Condition)
plot(eq_problem_shift_likert, center=3, ggtitle = "Eq Problem, shifts")
ggsave(filename = "Eq_Problem_shift.png", height=9)
```

## Step 7 - Statistical test for effect of condition using Beta Regression
First 